A Horrocks-type theorem for even orthogonal $K_2$

### 2021-02-10 dl-paper.tex
Fix misprints

\begin{theorem} \label{thm41} Suppose that $2 \in A^\times$. Then for $\ell \geq 7$ the canonical homomorphism $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{theorem}
\begin{proof}
 Consider the following commutative diagram with exact rows obtained from~\eqref{LodayRelativization}:
\[\begin{tikzcd} C(\rD_\ell, B, I) \arrow{r}{\lambda_B} \arrow[d, swap, "f", twoheadrightarrow] & \St(\rD_\ell, B, I) \arrow{r}{\mu_B} \arrow{d}[swap]{g} & \St(\rD_\ell, B) \arrow{r}{\nu_B} \arrow{d}[swap]{h} & \St(\rD_\ell, k[X^{-1}]) \arrow{d}[swap]{i} \\ C(\rD_\ell, R, I) \arrow{r}{\lambda_R} & \St(\rD_\ell, R, I) \arrow{r}{\mu_R} \arrow[ur, "t", dashrightarrow] & \St(\rD_\ell, R) \arrow{r}{\nu_R} & \St(\rD_\ell, k[X, X^{-1}]).\end{tikzcd}\]
The lifting $t$ in the above diagram is obtained from~\cref{lem:lemma32}.
Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$
 also lies in $\Ker(\nu_B)$ and hence comes from some $b \in \St(\rD_\ell, B, I)$ via $\mu_B$.
Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $\lambda_R(c) = g(b)$. 
By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, R, I)$.
The required assertion now follows from the following calculation:
 \[ 1 = \mu_B\lambda_B(d) = tg\lambda_B(d) = t\lambda_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
\end{proof}

@@

\subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor} \label{sec:V-construction}
Throughout this subsection $\Phi$ denotes an arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. 
\begin{df}\label{df:GM0_geq0}
Denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$. 
Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^\pm]$ and $A[X^\pm]\to R$:
\[\begin{tikzcd}[scale cd=0.8]
   G_M^0 \arrow[rr, "i_+^M", hookrightarrow] \arrow[dd, "i_-^M", hookrightarrow] \arrow[rd, hookrightarrow] & & \overline{\St}(\Phi, A[X], M[X]) \arrow[dd, "j_+^M", swap, near start] \arrow[rd, hookrightarrow] & \\ & \St(\Phi, A) \arrow[rr, "i_+", near start, hookrightarrow] \arrow[dd, "i_-", near start, hookrightarrow] & & \St(\Phi, A[X]) \arrow{dd}{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \arrow[rd, hookrightarrow] \arrow[rr, "j_-^M", near start] & & \overline{\St}(\Phi, R, I) \arrow[rd, hookrightarrow] & \\ & \St(\Phi, A[X\inv]) \arrow{rr}[swap]{j_-} & & \St(\Phi, R).
  \end{tikzcd}\]
Denote by $\overline{G}^{\geq 0}_M$ the image of the homomorphism $j_+^M$. \end{df}
Notice that the homomorphism $j_+^Mi_+^M$ is split by the homomorphism $ev^*_{X=1}$ of evaluation at $1$, therefore $G_M^0$ can be considered as a subgroup of $\overline{G}^{\geq 0}_M$.

>>>>

\begin{theorem} \label{thm41} Suppose that $2 \in A^\times$. Then for $\ell \geq 7$ the canonical homomorphism $\St(\rD_\ell, B) \to \St(\rD_\ell, R)$ is injective. \end{theorem}
\begin{proof}
 Consider the following commutative diagram with exact rows obtained from~\eqref{LodayRelativization}:
\[\begin{tikzcd} C(\rD_\ell, B, I) \arrow{r}{\lambda_B} \arrow[d, swap, "f", twoheadrightarrow] & \St(\rD_\ell, B, I) \arrow{r}{\mu_B} \arrow{d}[swap]{g} & \St(\rD_\ell, B) \arrow{r}{\nu_B} \arrow{d}[swap]{h} & \St(\rD_\ell, k[X^{-1}]) \arrow{d}[swap]{i} \\ C(\rD_\ell, R, I) \arrow{r}{\lambda_R} & \St(\rD_\ell, R, I) \arrow{r}{\mu_R} \arrow[ur, "t", dashrightarrow] & \St(\rD_\ell, R) \arrow{r}{\nu_R} & \St(\rD_\ell, k[X, X^{-1}]).\end{tikzcd}\]
The lifting $t$ in the above diagram is obtained from~\cref{lem:lemma32}.
Let $a$ be an element of $\Ker(h)$. Since $i$ is injective by~\cref{field-injectivity}, the element $a$
 also lies in $\Ker(\nu_B)$ and hence comes from some $b \in \St(\rD_\ell, B, I)$ via $\mu_B$.
Since $g(b) \in \Ker(\mu_R)$ there exists some $c \in C(\rD_\ell, R, I)$ such that $\lambda_R(c) = g(b)$. 
By~\cref{lem:prop41}, $f$ is surjective, therefore $c = f(d)$ for some $d \in C(\rD_\ell, B, I)$.
The required assertion now follows from the following calculation:
 \[ 1 = \mu_B\lambda_B(d) = tg\lambda_B(d) = t\lambda_Rf(d) =t(g(b)) = \mu_B(b) = a. \qedhere \]
\end{proof}

@@

\subsection{Construction of a \texorpdfstring{$\St(\Phi, B)$}{St(B)}-torsor} \label{sec:V-construction}
Throughout this subsection $\Phi$ denotes an arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. 
\begin{df}\label{df:GM0_geq0}
Denote the subgroup $\overline{\St}(\Phi, A, M)$ by $G_M^0$. 
Consider the following commutative diagram, in which the homomorphisms $i_\pm$ and $j_\pm$ are induced by the natural ring homomorphisms $A \to A[X^{\pm 1}]$ and $A[X^{\pm 1}]\to R$:
\[\begin{tikzcd}[scale cd=0.8]
   G_M^0 \arrow[rr, "i_+^M", hookrightarrow] \arrow[dd, "i_-^M", hookrightarrow] \arrow[rd, hookrightarrow] & & \overline{\St}(\Phi, A[X], M[X]) \arrow[dd, "j_+^M", swap, near start] \arrow[rd, hookrightarrow] & \\ & \St(\Phi, A) \arrow[rr, "i_+", near start, hookrightarrow] \arrow[dd, "i_-", near start, hookrightarrow] & & \St(\Phi, A[X]) \arrow{dd}{j_+} \\ \overline{\St}(\Phi, A[X\inv], M[X\inv]) \arrow[rd, hookrightarrow] \arrow[rr, "j_-^M", near start] & & \overline{\St}(\Phi, R, I) \arrow[rd, hookrightarrow] & \\ & \St(\Phi, A[X\inv]) \arrow{rr}[swap]{j_-} & & \St(\Phi, R).
  \end{tikzcd}\]
Denote by $\overline{G}^{\geq 0}_M$ the image of the homomorphism $j_+^M$. \end{df}
Notice that the homomorphism $j_+^Mi_+^M$ is split by the homomorphism $ev^*_{X=1}$ of evaluation at $1$, therefore $G_M^0$ can be considered as a subgroup of $\overline{G}^{\geq 0}_M$.
